Gut-resident microorganisms and their genes are associated with cognition and neuroanatomy in children

### 2023-10-18 manuscript/main.tex
fix citations format
fix acknowledgements sections

\usepackage{lineno}
\linenumbers
\usepackage{titlesec}
%\usepackage[none]{hyphenat} % use only if there is a problem
% Use Unicode characters
\usepackage[utf8]{inputenc}

\usepackage{scicite}
% Clean citations with biblatex
\usepackage[
backend=biber,
style=science
]{biblatex}

@@

\subsubsection*{Data and code availability}

@@

This research was funded by NIH UG3 OD023313 and Wellcome LEAP 1kD.
The authors declare that they have no competing interests.
We thank Libusha Kelly (Albert Einstein School of Medicine) and Daphne Koinis Mitchell (Brown University)
for helpful feedback on the manuscript. The research team also thanks the participants and families
of the participants who generously shared their time and samples for this project.

% https://credit.niso.org/

KSB, VKC, CH, and SD were responsible for conceptualization,
methodology and project administration.
VKC, SD, and VD were responsible for funding aqusition.
KSB, SHM, MB, FB, RCL, and JB contributed to data curation.
Formal analyses were conducted by KSB, GFB, and MB.
Investigation was performed by KSB, GFB, SHM, EW, FB, RCL, and MB.
Resources were provided by SHM, EW, FB, RCL, JB, CH, and MB.
Software and data visualizations were produced by KSB and GFB.
KSB, MB, SD, VD, and VKC were responsible for supervision.
Validation was performed by KSB, SHM, JB, and MB.
KSB and GFB wrote the initial draft, 
and review and editing were provided by SD, CH, and VKC.

>>>>

\usepackage{lineno}
\linenumbers
\usepackage{titlesec}
%\usepackage[none]{hyphenat} % use only if there is a problem
% Use Unicode characters
\usepackage[utf8]{inputenc}
\usepackage{enumitem}

\usepackage{scicite}
% Clean citations with biblatex
\usepackage[
backend=biber,
style=numeric,
maxbibnames=50
]{biblatex}

@@

@@

We thank Libusha Kelly (Albert Einstein School of Medicine) and Daphne Koinis Mitchell (Brown University)
for helpful feedback on the manuscript. The research team also thanks the participants and families
of the participants who generously shared their time and samples for this project.

\subsubsection*{Data and materials availability}

\subsubsection*{Funding}
This research was funded by NIH UG3 OD023313 and Wellcome LEAP 1kD.

\subsubsection*{Competing Interests}
The authors declare that they have no competing interests.

\subsubsection*{Author contributions}
% https://credit.niso.org/

\begin{itemize}[noitemsep]
    \item Conceptualization: KSB, VKC, CH, and SD
    \item Methodology: KSB, VKC, CH, and SD
    \item Project administraion: KSB, VKC, CH, and SD
    \item Funding acquisition: VKC, SD, and VD
    \item Data curation: KSB, GFB, SHM, MB, FB, RCL, and JB
    \item Formal analyses: KSB, GFB, and MB
    \item Investigation: KSB, GFB, SHM, EW, FB, RCL, and MB
    \item Resources: SHM, EW, FB, RCL, JB, CH, and MB
    \item Software and data visualizations: KSB and GFB
    \item Supervision: KSB, MB, SD, VD, and VKC 
    \item Validation: KSB, SHM, JB, and MB
    \item Initial draft: KSB and GFB
    \item Revision and editing: KSB, GFB, SD, CH, and VKC
\end{itemize}
